### 2024-09-14 Response/Response.tex

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} We formulate the task offloading problem as an MDP for time-sensitive tasks. This approach takes into account the dynamic nature of workloads at the ENs and concentrates on providing high performance in the MEC system while maximizing the long-term QoE.

	\item \textit{DRL-based Offloading Algorithm:} To address the problem of long-term QoE maximization, we focus on task completion, task delay, and energy consumption to quantify the MDs' QoE. We propose QECO algorithm based on DRL that empowers each MD to make offloading decisions independently, without prior knowledge of the other MDs' tasks and offloading models. With a focus on the MD's battery level, our approach leverages deep Q-network (DQN) \cite{mnih2015human} and long short-term memory (LSTM) \cite{hochreiter1997long} to prioritize and strike an appropriate balance between QoE factors. We also analyze the training convergence and complexity of the proposed algorithm.

	\item \textit{Performance Evaluation:} We conduct comprehensive experiments to evaluate the QECO's performance as well as its training convergence under different computation workloads. The results demonstrate that our algorithm quickly converges and effectively utilizes the processing capabilities of MDs and ENs, resulting in substantial improvement of at least 37\% in average QoE. This advantage is achieved through a 14\% increase in the number of completed tasks, along with 9\% and 6\% reductions in task delay and energy consumption, respectively, when compared to the potential game-based offloading algorithm (PGOA) \cite{yang2018distributed} and several benchmark methods.

\end{itemize}

The structure of this paper is as follows. Section~\ref{section:II} presents the system model, followed by the problem formulation in Section ~\ref{section:III}. In Section~\ref{section:IV}, we present the algorithm, while Section~\ref{section:V} provides an evaluation of its performance. Finally, we conclude in Section~\ref{section:VI}.

\section{System Model} 
\label{section:II}
\label{sec:latexhints}
% Required for proper example rendering in the compiled PDF
\newcount\LTGbeginlineexample
\newcount\LTGendlineexample
\newenvironment{ltgexample}%
{\LTGbeginlineexample=\numexpr\inputlineno+1\relax}%
{\LTGendlineexample=\numexpr\inputlineno-1\relax%
	%
	\tcbinputlisting{%
		listing only,
		listing file=\currfilepath,
		colback=green!5!white,
		colslot=green!25,
		coltitle=black!90,
		coltext=black!90,
		left=8mm,
		title=Corresponding \LaTeX{} code of \texttt{\currfilepath},
		listing options={%
			slot=none,
			language={[LaTeX]TeX},
			escapeinside={},
			firstline=\the\LTGbeginlineexample,
			lastline=\the\LTGendlineexample,
			firstnumber=\the\LTGbeginlineexample,
			basewidth=.5em,
			aboveskip=0mm,
			belowskip=0mm,
			numbers=left,
			xleftmargin=0mm,
			numberstyle=\tiny,
			numbersep=8pt%
		}
	}
}%
We investigate a MEC system consisting of a set of MDs denoted by $\mathcal{I} = \{1, 2, ..., I\}$, along with a set of ENs denoted by $\mathcal{J} = \{1, 2, ..., J\}$, where $I$ and $J$ represent the number of MDs and ENs, respectively. We regard time as a specific episode containing a series of $T$ time slots denoted by $\mathcal{T} = \{1, 2, \ldots, T\}$, each representing a duration of $\tau$ seconds. As shown in Fig.~\ref{fig1}, we consider two separate queues for each MD to organize tasks for local processing or dispatching to ENs, operating in a first-in-first-out (FIFO) manner. The MD's scheduler is responsible for assigning newly arrived tasks to each of the queues at the beginning of the time slot. On the other hand, we assume that each EN $j \in \mathcal{J}$ consists of $I$ FIFO queues, where each queue corresponds to an MD $i \in \mathcal{I}$. When each task arrives at an EN, it is enqueued in the corresponding MD's queue. %We assume that if a task is completed in a certain time slot, the next task in the queue will start its operation at the beginning of the next time slot.

\begin{figure}
	\captionsetup{name=Fig.}
	\centering
	\includegraphics[width=.7\linewidth]{Fig/queue}
	\vspace*{-1mm}
	\caption{An illustration of MD $i \in \mathcal{I}$ and EN $j \in \mathcal{J}$ in the MEC system.}
	\vspace*{-3mm}
	\label{fig1}
\end{figure}

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. The size of task $z_i(t)$ is selected from a discrete set $\Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\}$, where $\theta$ represents the number of these values. Hence, $\lambda_i(t) \in \Lambda \cup \{0\}$ to consider the case that no task has arrived. We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

We define two binary variables, $x_i(t)$ and $y_{i,j}(t)$ for $i \in \mathcal{I}$ and $j \in \mathcal{J}$ to determine the offloading decision and offloading target, respectively. Specifically, $x_i(t)$ indicates whether task $z_i(t)$ is assigned to the computation queue ($x_i(t) = 0$) or to the transmission queue ($x_i(t) = 1$), and $y_{i,j}(t)$ indicates whether task $z_i(t)$ is offloaded to EN $j \in \mathcal{J}$. If the task is dispatched to EN $j$, we set $y_{i,j}(t) = 1$; otherwise, $y_{i,j}(t) = 0$.

\subsection{Communication Model}
We consider that the tasks in the transmission queue are dispatched to the appropriate ENs via the MD wireless interface. We denote the transmission rate of MD $i$'s interface when communicating with EN $j \in \mathcal{J}$ in time $t$ as $r_{i,j}(t)$. In time slot $t \in \mathcal{T}$, if task $z_i(t)$ is assigned to the transmission queue for computation offloading, we define $l_i^{\text{T}}(t) \in \mathcal{T}$ to represent the time slot when the task is either dispatched to the EN or dropped. We also define $\delta_i^{\text{T}}(t)$ as the number of time slots that task $z_i(t)$ should wait in the queue before transmission. It should be noted that MD $i$ computes the value of $\delta_i^{\text{T}}(t)$ before making a decision. The value of $\delta_i^{\text{T}}(t)$ is computed as follows:
\begin{alignat}{1}
	\delta_i^{\text{T}}(t) =\textcolor{white}{i} \left[ \textcolor{white}{i}\max\limits_{t^{'}\textcolor{white}{i} \in \textcolor{white}{i} \{0,1,\ldots,t-1\}} l_i^{\text{T}}\textcolor{white}{i}(t^{'})-t+1\textcolor{white}{i}\right]^+\textcolor{white}{i},
	\label{1}  
\end{alignat}
where $[\cdot]^+ =$ max$(0, \cdot)$ and $l_i^{\text{T}}(0)=0$ for the simplicity of presentation. Note that the value of $\delta_i^{\text{T}}(t)$ only depends on $l_i^{\text{T}}(t)$ for $t' < t$. If MD $i \in \mathcal{I}$ schedules task $z_i(t)$ for dispatching in time slot $t \in \mathcal{T}$, then it will either be dispatched or dropped in time slot $l_i^{\text{T}}(t)$, which is
\begin{alignat}{1}
	l_i^{\text{T}}(t) = \min \Big\{t + \delta_i^{\text{T}}(t) + \lceil{D_i^{\text{T}}(t)}\rceil - 1, t + \Delta_i(t) - 1\Big\},
	\label{2}  
\end{alignat}
where $D_i^{\text{T}}(t)$ refers to the number of time slots required for the transmission of task $z_i(t)$ from MD $i \in \mathcal{I}$ to EN $j \in \mathcal{J}$. We have
\begin{alignat}{1}
	D_i^{\text{T}}(t) =  \sum_{\mathcal{J}} y_{i,j}(t) {\lambda_i(t) \over r_{i,j}(t)\tau}.
	\label{3}  
\end{alignat}
Let $E_i^{\text{T}}(t)$ denote the energy consumption of the transmission from MD $i \in \mathcal{I}$ to EN $j \in \mathcal{J}$. We have
\begin{alignat}{1}
	E_i^{\text{T}}(t) = D_i^{\text{T}}(t)p_i^{\text{T}}(t)\tau,
	\label{4}  
\end{alignat}
where $p_i^{\text{T}}(t)$ represents the power consumption of the communication link of MD $i \in \mathcal{I}$ in time slot $t$.
\subsection{Computation Model}
The computation tasks can be executed either locally on the MD or on the EN. In this subsection, we provide a detailed explanation of these two cases.
\subsubsection{Local Execution}
We model the local execution by a queuing system consisting the computation queue and the MD processor. Let $f_i$ denote the MD $i$'s processing power (in cycle per second). When task $z_i(t)$ is assigned to the computation queue at the beginning of time slot $t \in \mathcal{T}$, we define $l_i^{\text{C}}(t) \in \mathcal{T}$ as the time slot during which task $z_i(t)$ will either be processed or dropped. If the computation queue is empty, $l_i^{\text{C}}(t) = 0$. Let $\delta_i^{\text{C}}(t)$ denote the number of remaining time slots before processing task $z_i(t)$ in the computation queue. We have:
\begin{alignat}{1}
	\delta_i^{\text{C}}(t) = \left[ \max \limits_{t' \in \{0,1,\ldots,t-1\}} l_i^{\text{C}}(t')-t+1 \right]^+.
	\label{5}  
\end{alignat}
%In the above relation, the operator $[z]^+ = \max{0, z}$ is defined, and the variable $l_i^{\text{C}}(0) = 0$. Specifically, the expression $\max_{t' \in {0,1,2,\ldots,t-1}} l_i^{\text{C}}(t')$ determines the time slot until which all tasks placed in the local computation queue have been completed before time slot $t$. Therefore, $\delta_i^{\text{C}}(t)$ represents the number of time slots that task $z_i(t)$ needs to wait for processing. For example, suppose task $z_i(1)$ is in the computation queue, and its processing will be completed in time slot 5. Hence, $l_i^{\text{C}}(1) = 5$, meaning that the task should remain in the queue for $\Delta^{comp}(3) = [\max{5,0}-3+1]^+ = 3$ time slots until the process is finished.
In the equation above, the term $\max_{t' \in \{0, 1, \ldots, t-1\}} l_i^{\text{C}}(t')$ denotes the time slot at which each existing task in the computation queue, which arrived before time slot $t$, is either processed or dropped. Consequently, $\delta_i^{\text{C}}(t)$ denotes the number of time slots that task $z_i(t)$ should wait before being processed. We denote the time slot in which task $z_i(t)$ will be completely processed by $l_i^{\text{C}}(t)$ if it is assigned to the computation queue for local processing in time slot $t$. We have
\begin{alignat}{1}
	l_i^{\text{C}}(t) = \min \Big\{t + \delta_i^{\text{C}}(t) + \lceil D_i^{\text{C}}(t) \rceil - 1, t + \Delta_i(t) - 1\Big\}.
	\label{6}  
\end{alignat}
The task $z_i(t)$ will be immediately dropped if its processing is not completed by the end of the time slot $t + \Delta_i(t) - 1$. In addition, we introduce $D_i^{\text{C}}(t)$ as the number of time slots required to complete the processing of task $z_i(t)$ on MD $i \in \mathcal{I}$. It is given by:
\begin{alignat}{1}
	D_i^{\text{C}}(t) = { \lambda_i(t)  \over  f_i  \tau /  \rho_i(t)}.
	\label{7}  
\end{alignat}

%In particular, the processing of task $z_i(t)$ will commence at time $t + \delta_i^{\text{C}}(t)$. Therefore, the first component of the minimum operator is equal to the duration of time in which task $z_i(t)$ is completed without exceeding its deadline, denoted by $\delta_i^{\text{C}}(t)$. The second component refers to the duration of time in which task $z_i(t)$ becomes expired and discarded. As a result, $l_i^{\text{C}}(t)$ represents the time slot in which task $z_i(t)$ will be completed.
To compute the MD's energy consumption in the time slot $t \in \mathcal{T}$, we define $E_i^{\text{L}}(t)$ as:
\begin{alignat}{1}
	E_i^{\text{L}}(t) =  D_i^{\text{C}}(t) p_i^{\text{C}}  \tau, %=  { \lambda_i(t) \rho_i(t)  \over  f_i} p_i^{\text{C}},
	\label{8}  
\end{alignat}
where $p_i^{\text{C}} = 10^{-27}(f_i)^3$ represents the energy consumption of MD $i$'s CPU frequency \cite{mao2016dynamic}.
\subsubsection{Edge Execution}
We model the edge execution by the queues associated with MDs deployed at ENs. If computation task $z_i(t')$ is dispatched to EN $j$ in time $t' < t$, we let $z_{i,j}^{\text{E}}(t)$ and $\lambda_{i,j}^{\text{E}}(t)$ (in bits) denote the unique index of the task and the size of the task in the $i^{\text{th}}$ queue at EN $j$. We define $\eta_{i,j}^{\text{E}}(t)$ (in bits) as the length of this queue at the end of time slot $t \in \mathcal{T}$. We refer to a queue as an active queue in a certain time slot if it is not empty. That being said, if at least one task is already in the queue from previous time slots or there is a task arriving at the queue, that queue is active. We define $\mathcal{B}_j(t)$ to denote the set of active queues at EN $j$ in time slot $t$.
\begin{alignat}{1}
	\mathcal{B}_j(t) = \textcolor{white}{i}\Big\{i \textcolor{white}{i}\big| i \in \mathcal{I}, \lambda_{i,j}^{\text{E}}(t)>0\,\, \textcolor{white}{i}\text{or}\textcolor{white}{i} \,\, \eta_{i,j}^{\text{E}}(t-1)>0\textcolor{white}{i}\Big\}.\textcolor{white}{i}
	\label{9}  
\end{alignat}
We introduce $b_j(t) \triangleq |\mathcal{B}_j(t)|$ that represents the number of active queues in EN $j \in \mathcal{J}$ in time slot $t \in \mathcal{T}$. In each time slot $t \in \mathcal{T}$, the EN's processing power is divided among its active queues using a generalized processor sharing method~\cite{parekh1993generalized}. Let variable $f_j^{\text{E}}$ (in cycles per second) represent the computational capacity of EN $j$. Therefore, EN $j$ can allocate computational capacity of $f_j^{\text{E}}/(\rho_i(t) b_j(t))$ to each MD $i \in \mathcal{B}_j(t)$ during time slot $t$. To calculate the length of the computation queue for MD $i \in \mathcal{I}$ in EN $j \in \mathcal{J}$, we define $\omega_{i,j}(t)$ (in bits) to represent the number of bits from dropped tasks in that queue at the end of time slot $t \in \mathcal{T}$. The backlog of the queue, referred to as $\eta_{i,j}^{\text{E}}(t)$ is given by:
\begin{alignat}{1}
	\eta_{i,j}^{\text{E}}(t)\hspace{-0.8mm}=\hspace{-1mm}\left[\eta_{i,j}^{\text{E}}(t-1)\hspace{-0.6mm}+\hspace{-0.7mm}\lambda_{i,j}^{\text{E}}(t)\hspace{-0.7mm}-\hspace{-0.7mm}{f_j^{\text{E}}\tau\over \rho_i(t)b_j(t)} -\omega_{i,j}(t)\right]^+\hspace{-1mm}.
	\label{10}  
\end{alignat}
We also define $l_{i,j}^{\text{E}}(t) \in \mathcal{T}$ as the time slot during which the offloaded task $z_{i,j}^{\text{\text{E}}}(t)$ is either processed or dropped by EN $j$. Given the uncertain workload ahead at EN $j$, neither MD $i$ nor EN $j$ has information about $l_{i,j}^{\text{E}}(t)$ until the corresponding task $z_{i,j}^{\text{E}}(t)$ is either processed or dropped. Let $\hat{l}_{i,j}^{\text{E}}(t)$ represent the time slot at which the execution of task $z_{i,j}^{\text{E}}(t)$ starts. In mathematical terms, for $i \in \mathcal{I}$, $j \in \mathcal{J}$, and $t \in \mathcal{T}$, we have:
\begin{alignat}{1}
	\hat{l}_{i,j}^{\text{E}}(t) = \max \{t, \max \limits_{t^{'} \in \{0,1,\ldots,t-1\}} l_{i,j}^{\text{E}}(t^{'})+1\},
	\label{11}  
\end{alignat}
where $l_{i,j}^{\text{E}}(0) = 0$. Indeed, the initial processing time slot of task $z_{i,j}^{\text{E}}(t)$ at EN should not precede the time slot when the task was enqueued or when the previously arrived tasks were processed or dropped. Therefore, $l_{i,j}^{\text{E}}(t)$ is the time slot that satisfies the following constraints. %For $i \in \mathcal{I}$, $j \in \mathcal{J}$, and $t \in \mathcal{T}$,
\begin{alignat}{1}
	\sum_{t^{'}=\hat{l}_{i,j}^{\text{E}}(t)}^{l_{i,j}^{\text{E}}(t)}{f_j^{\text{E}}\tau \over \rho_i(t)b_j(t^{'})}\mathbbm{1}(i \in \mathcal{B}_j(t^{'}))  \geq   \lambda_{i,j}^{\text{E}}(t),
	\label{12}  \\
	\sum_{t^{'}=\hat{l}_{i,j}^{\text{E}}(t)}^{l_{i,j}^{\text{E}}(t)-1}{f_j^{\text{E}}\tau \over \rho_i(t)b_j(t^{'})}\mathbbm{1}(i \in \mathcal{B}_j(t^{'})) < \lambda_{i,j}^{\text{E}}(t),
	\label{13}  
\end{alignat}
